The ChEMBL database as Linked Open Data

### 2012-03-11 article.tex
Added initial text about the ChemSpider link (by Antony)

>>>>

RSC’s ChemSpider~\cite{Pence2010} is a free online database of over 26 million unique
chemical compounds aggregated from over 400 data sources as well as chemical data extracted
from RSC scientific articles and databases. Since its inception efforts have been made to
utilize the platform as both a deposition platform for the community to contribute data as
well as a platform for annotation and curation. Studies have shown that there are data
quality issues in many of the public compound databases~\cite{Williams2011} and ChemSpider has become a
valuable resource for curated data, especially chemical-compound name mappings. ChemSpider
is presently providing the chemical services underpinning the Open PHACTS semantic web
project~\cite{Williams2012} providing access to structure, substructure and similarity searching services
to the core architecture of the project. Specific chemical data sources containing data
mappings between ChemSpider identifiers (CSIDs) and the original data source identifiers
have been provided to the triple store, together with chemical identifiers including
validated chemical names (systematic, generic and trivial), SMILES () and InChIs (). 
The data mappings between the ChemSpider IDs and the data source IDs are released to
the community under Creative Commons licenses (CC-BY-SA 3.0). Link mappings of the
form:

\begin{tiny}
\begin{verbatim}
<http://rdf.chemspider.com/370>
 skos:exactMatch
 <http://data.kasabi.com/dataset/chembl-rdf/chemblid/CHEMBL324846>
\end{verbatim}
\end{tiny}

have been constructed.
